{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-14 thesis/landslide.tex
minor fixups landslide.tex

This chapter will discuss Landslide's outer and inner workings in all their gory detail.
It is intended for the aspiring developer or the ambitious user
and hence unlike other chapters is written in the style of documentation rather than as a report of research results.

@@

\section{Algorithms of note}

% not worth discussing?
%\subsection{Kernel annotations}
%\subsection{Bug identification}

@@

The set intersection is implemented in {\tt mem\_shm\_interseect()} in {\tt memory.c}.
It checks for read/write and write/write pairs to the same address with an $O(\mathsf{max}(m,n))$ scan of both access sets (pre-sorted).
If any address $a$ exists with $a \in M(t_i)$ and $a \in M(t_j)$ and $M(t_i)(a) = \mathsf{write} \vee M(t_j)(a) = \mathsf{write}$
then $t_i$ and $t_j$ are said to conflict,
which I will denote $t_i \leftrightsquigarrow_S t_j$.

@@

\subsubsection{Accuracy example}

@@

		Under RE, the estimate at \dporTA{{\tt tmp1++}} will be 9 seconds
		(incorrectly assuming $\bigstar$1's subtree will be 1 branch),
		and the root estimate will be 20 seconds, an underestimate.
	\item After branch B, $\bigstar$2 is now marked.
		Under WBE, the subtree estimate at \dporTB{{\tt tmp2++}} is 1/2,
		which at \dporTA{{\tt tmp1++}} is then divided by its $\mathsf{marked~children}$
		and added to its estimate, yielding 3/4.
		Note that it has ``forgotten'' that only branch A, alone, contributed to its original 1/2,
		rather than two branches as in this subtree.
		The root
		the subtree estimate at \dporTA{{\tt tmp1++}} is updated (and propagated down) to 3/8.
		Dividing the current progress (2) by that yields 5.33 branches, an underestimate.

>>>>

This chapter will discuss Landslide's outer and inner workings in all their gory detail.
It is intended for the aspiring developer or the ambitious user
and hence unlike other chapters is written in the style of documentation rather than as a report of research results.
The reader interested only in a theoretical introduction to model checking's foundational algorithms,
with detailed and friendly examples to help establish intuitions the later chapters may require,
may skip to \sect{\ref{sec:landslide-algs}}.

@@

\section{Algorithms}
\label{sec:landslide-algs}

This section describes Landslide's model-checking algorithms from a theoretical perspective.
The more complex ones are accompanied by concrete examples to hopefully help the reader build a solid intuition,
which upcoming chapters will require in their soundness proofs.

@@

The set intersection is implemented in {\tt mem\_shm\_intersect()} in {\tt memory.c}.
It checks for read/write and write/write pairs to the same address with an $O(\mathsf{max}(m,n))$ scan of both access sets (pre-sorted).
If any address $a$ exists with $a \in M(t_i)$ and $a \in M(t_j)$ and $M(t_i)(a) = \mathsf{write} \vee M(t_j)(a) = \mathsf{write}$
then $t_i$ and $t_j$ are said to conflict,
which I will denote $t_i \leftrightsquigarrow_S t_j$.

@@

@@

		Under RE, the estimate at \dporTA{{\tt tmp1++}} will be 9 seconds
		(incorrectly assuming $\bigstar$1's subtree will be 1 branch),
		and the root estimate will be 20 seconds, an underestimate.
	\item After branch B, $\bigstar$2 is now marked.
		Under WBE, the subtree estimate at \dporTB{{\tt tmp2++}} is 1/2,
		which at \dporTA{{\tt tmp1++}} is then divided by its $\mathsf{marked~children}$
		and added to its estimate, yielding 3/4.
		Note that it has ``forgotten'' that only branch A, alone, contributed to its original 1/2,
		rather than two branches as in this subtree.
		The root and \dporTA{{\tt tmp1++}}'s subtree estimates are updated (and propagated down) to 3/8.
		Dividing the current progress (2) by that yields 5.33 branches, an underestimate.
